### 2013-11-12 paper/mcmc.tex
Fix figure paths

Before attempting solving the inverse problem,
we need to make sure that the observed data are
comparable to the simulated one.
To this end, Figure~\ref{fig:compare}
compares PC mean water surface elevation profiles
with their counterparts from the observed gauge locations.
The plots show good agreement between the simulations and the observations at different
locations and at different times. 
%

Figure~\ref{fig:compare} can be recast as a scatter plot shown in 
Figure~\ref{fig:scatter}.

@@

@@

>>>>

Before attempting solving the inverse problem,
we need to make sure that the observed data are
comparable to the simulated one.
To this end, Figure~\ref{fig:compare}
compares PC mean water surface elevation profiles
with their counterparts from the observed gauge locations.
The plots show good agreement between the simulations and the observations at different
locations and at different times. 
%
\begin{figure}[h]
\begin{tabular}{clc}
%        
\includegraphics[width=0.475\textwidth]{./figures/compare1.pdf} &
\includegraphics[width=0.475\textwidth]{./figures/compare2.pdf} \\
\includegraphics[width=0.475\textwidth]{./figures/compare3.pdf} &
\includegraphics[width=0.475\textwidth]{./figures/compare4.pdf}
\end{tabular}
\caption{Comparison of PC mean 
and observed data of water surface elevation with time at the four gauges.}
\label{fig:compare}
\end{figure}

Figure~\ref{fig:compare} can be recast as a scatter plot shown in 
Figure~\ref{fig:scatter}.
\begin{figure}[h]
\centering
\includegraphics[width=0.475\textwidth]{./figures/scatter.pdf} 
\caption{Scatter plot of PC mean water surface elevation vs. observed ones.}
\label{fig:scatter}

\end{figure}

@@

\begin{figure}[h]
\begin{tabular}{clc}
\includegraphics[width=0.475\textwidth]{./figures/chain_p1.pdf} &
\includegraphics[width=0.475\textwidth]{./figures/chain_p2.pdf} \\
\includegraphics[width=0.475\textwidth]{./figures/chain_p3.pdf} &
\includegraphics[width=0.475\textwidth]{./figures/chain_s1.pdf}
\end{tabular}
\caption{Chain samples for the three Manning's roughness coefficients $N_1,N_2,N_3$ and $\sigma^2$
the variance between simulations and observations.}
\label{fig:mcmc} 
\end{figure}

@@

 \begin{figure}[h]
        \begin{tabular}{clc}
\includegraphics[width=0.475\textwidth]{./figures/pdf_p1.pdf} &
\includegraphics[width=0.475\textwidth]{./figures/pdf_p2.pdf} \\
\includegraphics[width=0.475\textwidth]{./figures/pdf_p3.pdf} &
\includegraphics[width=0.475\textwidth]{./figures/pdf_s1.pdf}
        \end{tabular}
        \caption{Posterior distributions for the three Manning's roughness coefficients $N_1,N_2,N_3$ 
and $\sigma^2$ the variance between simulations and observations.}
\label{fig:pdfs} 
        \end{figure}

### 2013-11-12 paper/tsunami.tex
major changes to formulation part
removed figures from tsnumai.tex
Fix figure paths

@@

\begin{figure}[h]
\centering
\begin{tabular}{clc}
\includegraphics[width=0.45\textwidth]{../figures/topo.pdf}  &
\includegraphics[width=0.45\textwidth]{../figures/coef.pdf} 
\label{setup}
\end{tabular}
\caption{Topography and gauge locations.}
\label{fig:setup}
\end{figure}
\subsection{Parametric Uncertainty}
\subsection{Observations}
During this tsunami, different gauges were installed to observed the surface elevation
The locations of theses gauges are shown in Figure~\ref{setup} .
The gauges are used in the inverse problem to infer the manning coefficients.

\begin{figure}[h]      
\centering
\includegraphics[width=0.6\textwidth]{../figures/obs.pdf}
\caption{Observed data of water surface elevation with time at four different gauges.}
\label{fig:obs}
\end{figure}

>>>>

%!TEX root = paper.tex

Background literature so far
\begin{itemize}
    \item Myers and Baptista (2001) - Crude friction coefficient sensitivity, found it to be important but not fully explored
    \item Jakeman et al (2010) - Again a crude (two coefficient) sensitivity analysis.
    \item Dao and Tkalich (2007) - Really not a very good paper, also crude SA.
\end{itemize}

\section{Numerical Model}

@@

\begin{figure}[h]
\centering
\begin{tabular}{clc}
\includegraphics[width=0.45\textwidth]{./figures/topo.pdf}  &
\includegraphics[width=0.45\textwidth]{./figures/coef.pdf} 
\label{setup}
\end{tabular}
\caption{Topography and gauge locations.}
\label{fig:setup}
\end{figure}

\subsection{Parametric Uncertainty}

\subsection{Observations}

Observations used in th

During this tsunami, different gauges were installed to observed the surface elevation
The locations of theses gauges are shown in Figure~\ref{setup} .
The gauges are used in the inverse problem to infer the manning coefficients.

\begin{figure}[h]      
\centering
\includegraphics[width=0.6\textwidth]{./figures/obs.pdf}
\caption{Observed data of water surface elevation with time at four different gauges.}
\label{fig:obs}
\end{figure}
